Addressing climate change and development pressures in an urban estuary through habitat restoration planning

### 2022-08-05 manu-draft.qmd
adding alluvial plots

@@

@@

@@

>>>>

Figure @fig-gisworkflow

@@

Figure @fig-subtchgdatalluv

@@

Figure @fig-chgdatalluv

@@

## Figures

![Spatial analysis workflow used to identify opportunity areas for habitat conservation and restoration in the Tampa Bay watershed. Workflows are divided into binning of land use/land cover categories into relevant habitat types and spatial overlay of datasets to identify the opportunity areas.](figs/gisworkflow.png){#fig-gisworkflow fig-align="center"}

![Change analysis of habitat categories in the subtidal strata of the Tampa Bay watershed.  The left column shows relative areas in 1988 and the right column shows relative areas in 2018 for each habitat category. The grey lines show the proportional change of each habitat category between the years.](figs/subtchgdatalluv.png){#fig-subtchgdatalluv fig-align="center"}

![Change analysis of habitat categories in the intertidal and supratidal strata of the Tampa Bay watershed.  The left column shows relative areas in 1990 and the right column shows relative areas in 2017 for each habitat category. The grey lines show the proportional change of each habitat category between the years.](figs/chgdatalluv.png){#fig-chgdatalluv fig-align="center"}

Figure 4: Map of opportunity assessment

Figure 5: Map of restoration potential

## Tables

Table 1: Land use change table

Table 2: Subtidal change table

Table 3: Summary of the opportunity assessment analysis

Table 4: Targets
